RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-31 casestudies.tex
try

To illustrate some aspects of RCloud, we present an example application
for stock price analysis.\footnote{Unfortunately we could not include
production notebooks containing proprietary or personal information.}
The example, although simplified, shows key steps in the development
and deployment process we intend to support.

>>>>

To illustrate some aspects of RCloud, we present an example application
for stock price analysis.\footnote{Unfortunately this report could not
include production notebooks containing proprietary or personal information.}
The example, although simplified, shows key steps in the development
and deployment process we intend to support.

### 2014-03-31 system.tex
try

\subsection{Interactive notebooks, etc.}

@@

In addition, R is naturally better as a language for analysis, and
JavaScript as a language for interactive visualization.  To draw on
the strengths of both languages and both environments, the connection
between the languages is not just procedural: it makes \emph{closures}
and \emph{first-class functions} available across the network link.
This provides great flexibility, so that for example, a chart built
with dc.js or leaflet.js can call back to analysis functions in R
without having to formalize the protocol between the processes.

@@

There exists a URL for every notebook in RCloud, and notebooks by
default are visible by the entire organization. This is deliberate.
As pointed out by Wattenberg and Kriss~\cite{Wattenberg:2011:DFS},
broad access to analysis outputs (in their case, for NameVoyager)
increases long-term engagement in part through cross-references on
the web. Although our prototype RCloud deployment is only visible
inside a corporate intranet, we nevertheless found anecdotal support
for this notion by discovering links to RCloud notebooks in internal
discussion fora and mailing lists.

>>>>

\subsection{Interactive notebooks\label{sec:notebooks}}

@@

In addition, R is well suited as a language for analysis, and
JavaScript for interactive visualization. To draw on
the strengths of both languages and both environments, the connection
between the languages is not just procedural: it makes \emph{closures}
and \emph{first-class functions} available across the network.
This provides considerable flexibility, so that for example, a chart built
with dc.js or leaflet.js can call back to analysis functions in R
without having to formalize the protocol between the processes.

@@

Every notebook in RCloud is named by a URL, and notebooks by
default are visible by the entire organization. This is deliberate.
As pointed out by Wattenberg and Kriss~\cite{Wattenberg:2011:DFS},
broad access to analysis outputs (in their case, for NameVoyager)
increases long-term engagement in part through cross-references on
the web. Although our prototype RCloud deployment is only visible
inside a corporate intranet, we nevertheless found anecdotal support
for this notion by discovering links to RCloud notebooks in internal
discussion fora and mailing lists.
